\documentclass{article}[10pt]
\usepackage{upgreek}
\usepackage{hyperref}
\usepackage{verbatim}
%\href{http://pen.phys.virginia.edu/restricted/group_meet/20101102agenda.txt}{link to agenda}

% github desktop test
% github desktop test 2


\begin{document}
\begin{center}
{\LARGE \textbf{Loreto Peter Alonzi III} }

\vspace{0.5cm}

\begin{tabular}{lclr}
\hline
\hline
\href{https://datascience.virginia.edu/}{School of Data Science}         & \qquad \qquad &  &         \\
\href{virginia.edu}{University of Virginia}        & \qquad \qquad &Phone: &   (434) 924-7835      \\
1919 Ivy Road, rm 344              & \qquad \qquad & Email: & alonzi@virginia.edu \\
Charlottesville, VA 22903& \qquad \qquad &        &                     \\
\hline
\hline
\end{tabular}
\end{center}

\section*{Professional Experience}
\begin{itemize}
\item [$\bullet$] Assistant Professor of Data Science, General Faculty, University of Virginia, 2022-present
\item [$\bullet$] Open Data Lab Project Manager and Data Scientist, School of Data Science, University of Virginia, 2018-2022
\item [$\bullet$] Senior Research Data Scientist, Research Data Services, University Library, 2014-2018
\item [$\bullet$] Postdoctoral Research Associate, University of Washington, Department of Physics, Center for Experimental Nuclear Physics and Astrophysics, 2012-2014
\end{itemize}


\section*{Education}
\begin{itemize}
\item [$\bullet$] Ph.D. Physics, \href{http://www.phys.virginia.edu/}{\emph{University of Virginia}}, 2012.
\item [$\bullet$] M.A. Physics, \emph{University of Virginia}, 2007.
\item [$\bullet$] B.S. Physics with Honors et Magna cum Laude, \href{http://www.wm.edu/}{\emph{The College of William and Mary in Virginia}}, 2005.
\end{itemize}

%-----------------------------------------------------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------------------------------------

\section*{Teaching Experience}
\subsection*{\emph{Selected Courses}}
\begin{itemize}
\item [$\bullet$] University of Virginia - DS 1001 - Foundations of Data Science - Spring 2024 
\item [$\bullet$] University of Virginia - DS 1001 - Foundations of Data Science - Fall 2023 
\item [$\bullet$] University of Virginia - DS 1001 - Foundations of Data Science - Spring 2023 (New Course, co-designed with B. Wright)
\item [$\bullet$] University of Virginia - DS 4002 - Data Science Project Course - Fall 2023
\item [$\bullet$] University of Virginia - DS 4002 - Data Science Project Course - Spring 2023
\item [$\bullet$] University of Virginia - DS 4002 - Data Science Project Course - Fall 2022
\item [$\bullet$] University of Virginia - BME 6550 - A1 Data Science - 2021
\item [$\bullet$] University of Virginia - DS 6559 - Data Wrangling in Python - 2015,2016
\item [$\bullet$] University of Virginia - DS 6501 - Data Wrangling in Python - 2018
\item [$\bullet$] University of Virginia - DS 6999 - Independent Study - 2018
\item [$\bullet$] University of Virginia - PHYS 241W - Physics Workshop - 2005
\end{itemize}
Full record see: \href{https://github.com/alonzi/cv/blob/master/teaching-record.md}{github.com/alonzi/cv}

%-----------------------------------------------------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------------------------------------

\section*{Funded Grant Proposals as PI/Co-PI}
\begin{itemize}
\item[$\bullet$] Building Inclusive Student-Informed Courses (2023) \$9,600
\begin{itemize}
\item[$\bullet$] (PI) R. Schmidt; (Co-PI): {\bf L.P.Alonzi}
\item[$\bullet$] Inclusive Excellence award from UVA Division for Diversity, Equity, and Inclusion
\end{itemize}
\item[$\bullet$] Data Science Active Learning Lab (2022) \$150,000
\begin{itemize}
\item[$\bullet$] (PI) B.Wright; (Co-PI): {\bf L.P.Alonzi}
\item[$\bullet$] President and Provost’s Fund for Institutionally Related Research
\end{itemize}
\item[$\bullet$] Optimizing pediatric donor heart utilization using big data analytics (2022) \$133,078
\begin{itemize}
\item[$\bullet$] (PI) M.McCulloch; (Co-PI): {\bf L.P.Alonzi}, M. Porter
\item[$\bullet$] Jefferon Trust
\end{itemize}
\item[$\bullet$] SIWIF: Summer Institute on Wigner Imaging and Femtography (2019) \$50,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2020-FEMT-006-05 (continuation supplemental)
\end{itemize}
\item[$\bullet$] SIWIF: Summer Institute on Wigner Imaging and Femtography (2019) \$30,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2020-FEMT-006-05
\end{itemize}
\end{itemize}\begin{itemize}
\item[$\bullet$] Wigner Imaging (2018) \$50,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2019-FEMT-002-04
\end{itemize}
\end{itemize}

\section*{Selected Publications}
\subsection*{\emph{Journal Articles}}
\begin{itemize}
\item [$\bullet$] M.A.McCulloch, {\bf L. P. Alonzi}, S. C. White, F. Haregu, and M. D. Porter. “Pediatric Donor Heart Acceptance Practices in the United States: What Is Really Being Considered?” Pediatric Transplantation 28, no. 1 (November 2023). https://doi.org/10.1111/petr.14649.
\item [$\bullet$] B. Abi, et al. "Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm" (Muon $g-2$ Collaboration) Phys. Rev. Lett. 126, 141801 (2021)
\item [$\bullet$] J. Grigsby, et al. "Deep learning analysis of deeply virtual exclusive photoproduction" Phys. Rev. D 104, 016001 (2021)
\item [$\bullet$] D. Blyth, et al. "First Observation of P-odd $\gamma$ Asymmetry in Polarized Neutron Capture on Hydrogen" (NPDGamma Collaboration) Phys. Rev. Lett. 121, 242002 (2018)
\item [$\bullet$] D. Po\v{c}ani\'c, et al. "PEN: a low energy test of lepton universality", \emph{PoS HQL} 2016 (2017) 042
\item [$\bullet$] {\bf L.P.Alonzi}, et al. "The calorimeter system of the new muon $g-2$ experiment at Fermilab", \emph{Nucl.Instrum.Meth. A} 824 (2016) 718-720
\item [$\bullet$] Muon $g-2$ collaboration, "The Measurement of the Anomalous Magnetic Moment of the Muon at Fermilab", \emph{J.Phys.Chem.Ref.Data} 44 (2015) no.3, 031211
\item [$\bullet$] A.T. Fienberg, et al. "Studies of an array of PbF2 Cherenkov crystals with large-area SiPM readout", \emph{Nucl.Instrum.Meth. A} 783 12-21 (2015)
%\item [$\bullet$] D. Po\v{c}ani\'c, et al. ``Nab: Measurement Principles, Apparatus and Uncertainties'', \href{http://www.sciencedirect.com/science?_ob=ArticleURL&_udi=B6TJM-4WY6JS6-B&_user=709071&_coverDate=12/11/2009&_rdoc=1&_fmt=high&_orig=search&_origin=search&_sort=d&_docanchor=&view=c&_searchStrId=1563612201&_rerunOrigin=google&_acct=C000039638&_version=1&_urlVersion=0&_userid=709071&md5=602265f8ed1e05dbcd605115545a0871&searchtype=a}{\emph{Nucl.Instrum.Meth. A} 611, 211-215} (2009).
\end{itemize}




\section*{Presentations}

\subsection*{\emph{Invited Talks}}

\begin{itemize}
\item [$\bullet$] "Introduction to R", DAACS Open Academy, Fall 2021
\item [$\bullet$] "What Entropy and Impendance Mean in Data Science", Jefferson Lab AI Lunch Series, November 2020
\item [$\bullet$] "Machine Learning for global fitting of CFF from sparse data", Data Science Roadmap to compton form factors of quarks and gluons, Center for Nuclear Femtography, September 2020.
\item [$\bullet$] "Data Science and Femtography", CNF2019 Symposium, SURA Headquarters, August 2019.
\item [$\bullet$] "Intro to Data Science", CSInstitute, July 2019.
\item [$\bullet$] ``The New Muon g-2 Experiment: E989 Status and Progress Update'', SESAPS 81st annual meeting, November 2014.
\item [$\bullet$] ``Using the Library to Advance Scientific Data Practices'', University of Virginia, July 2014.
\item [$\bullet$] L.P. Alonzi for the PEN Collaboration, ``Precision Measurements of Rare Pion Decay Channels'', University of Washington, CENPA, March 2012.
%\item [$\bullet$] L.P. Alonzi for the Nab Collaboration, ``Precision Measurement of \emph{a} and \emph{b} in Neutron Beta Decay'', University of Virginia, January 2009.
\end{itemize}


\section*{Research Experience}
\begin{itemize}
\item [$\bullet$] Research Associate, Professor David Hertzog (\emph{UW}), June 2012-September 2014.
\begin{itemize}
\item [$\circ$] \href{http://muon-g-2.fnal.gov/collaboration.shtml}{The New Muon g-2 Collaboration: E989}
\end{itemize}
\item [$\bullet$] Research Assistant, Professor Dinko Po\v{c}ani\'c (\emph{UVa}), June 2007-May 2012.
\begin{itemize}
\item [$\circ$] \href{https://en.wikipedia.org/wiki/NPDGamma_experiment}{The NPD$\gamma$ Collaboration}
\item [$\circ$] \href{http://pen.phys.virginia.edu/}{The PEN Collaboration}
\item [$\circ$] \href{http://nab.phys.virginia.edu/}{The Nab Collaboration}
\end{itemize}
\item [$\bullet$] Honors Thesis, Professor William Kossler (\emph{W\&M}), 2004-2005.
\end{itemize}






\section*{Committee Service}
\begin{itemize}
\item [$\bullet$] 2023 Innovations in Pedagogy Summit, CTE, Charlottesville VA
\item [$\bullet$] Academic Committee, UVADS, Charlotteville VA
\item [$\bullet$] Annual Meeting Program Committee, ADSA, Ann Arbor MI
\item [$\bullet$] Undergraduate Committee, UVADS, Charlotteville VA
\end{itemize}




\section*{Honors and Awards}
\begin{itemize}
\item [$\bullet$] University of Virginia Society of Fellows, Junior Fellow, 2010.
\item [$\bullet$] Eagle Scout, BSA NEIC Troop 5, 1999.
\end{itemize}













\begin{comment}


\subsection*{\emph{Contributed Talks}}
\begin{itemize}
\item [$\bullet$] L.P. Alonzi for the g-2 Collaboration, \href{http://pen.phys.virginia.edu/lpa2a-docs/2014-05-02-Alonzi-APSNWSection.pdf}{``The New Muon g-2 Experiment: E989 Status and Progress Update''}, \emph{APS NW Section Meeting} (2014).
\item [$\bullet$] L.P. Alonzi for the PEN Collaboration, \href{http://pen.phys.virginia.edu/talks/2010_April_APS_alonzi.pdf}{``A Mini Time Projection Chamber of the PEN Experiment''}, \emph{April APS Meeting} (2010).
\item [$\bullet$] L.P. Alonzi for the Nab Collaboration, \href{http://nab.phys.virginia.edu/slides/2009_April_APS_Alonzi.pdf}{``Precision Measurement of \emph{a} and \emph{b} in Neutron Beta Decay: The Nab/abBA Experimental Program''}, \emph{April APS Meeting} (2009).
\end{itemize}


\section*{Relevant Skills}
\begin{itemize}
\item [$\bullet$]Programming: Python, Git, MachineLearning, Data Mining, BASH, C++, AWK, Mathematica, ROOT (data analysis package), GEANT4, LaTeX, Microsoft Office.
\item [$\bullet$]Statistics and Analysis: Monte Carlo Techniques, Simulation, Model Fabrication, Data visualizations, Regression,$\chi^2$,Maximum Likelihood, Bootstrap, Fitting, Extrapolation
\item [$\bullet$]Operating Systems:  Linux/Unix, Windows, and Mac
\end{itemize}










\section*{Research Experience}
\begin{itemize}
\item [$\bullet$] Research Associate, Professor David Hertzog (\emph{UW}), June 2012-September 2014.
\begin{itemize}
\item [$\circ$] \href{http://muon-g-2.fnal.gov/collaboration.shtml}{The New Muon g-2 Collaboration: E989}, 2012-2016.
\end{itemize}
\item [$\bullet$] Research Assistant, Professor Dinko Po\v{c}ani\'c (\emph{UVa}), June 2007-May 2012.
\begin{itemize}
\item [$\circ$] \href{http://pen.phys.virginia.edu/}{The PEN Collaboration}, 2007-present.
\item [$\circ$] \href{http://nab.phys.virginia.edu/}{The Nab Collaboration}, 2007-present.
\end{itemize}
\item [$\bullet$] Honors Thesis, Professor William Kossler (\emph{W\&M}), 2004-2005.
\end{itemize}
\section*{Honors and Awards}
\begin{itemize}
\item [$\bullet$] University of Virginia Society of Fellows, Junior Fellow, 2010.
\item [$\bullet$] Eagle Scout, BSA NEIC Troop 5, 1999.
\end{itemize}

\vspace{0.5cm}
\vspace{0.5cm}
References are available by request.

\end{comment}

\begin{center} Updated: \today \end{center}



\end{document}


%\section*{University Partnerships}
%\begin{itemize}
%\item [$\bullet$] UVA Data Science Institute (DSI): Currently serving as a staff Data Scientist
%\item [$\bullet$] Computation and Data Resource Exchange (CADRE): Chair of the education subcommittee
%\item [$\bullet$] Claude Moore Health Science Library (HSL): Currently working on a joint data analysis project, Served on a dual search committee
%\item [$\bullet$] School of Medicine Research Computing (SOMRC): Orchestrating a partnership with DSI to provide Amazon Web Services (AWS) to UVA users
%\item [$\bullet$] Research Computing Infrastructure (RCI): Working with this group to provide access and support of computer resrouces like Ivy and Rivanna to researchers 
%\end{itemize}

%\section*{Management Roles}
%\begin{itemize}
%\item [$\bullet$] Senior Research Data Scientists: Supervised two staff members prior to Library Reorganization
%\item [$\bullet$] Postdoctoral Research Associate, University of Washington: Supervised laboratory operations for graduate and undergraduate studtents. 
%\end{itemize}

%\subsection*{\emph{Experiment Proposals}}
%\begin{itemize}
%\item [$\bullet$] \href{http://nab.phys.virginia.edu/nab_proposal.pdf}{Precise Measurement of the Neutron Beta Decay Parameters ``a'' and ``b'': The \emph{Nab} Experiment} (2007)
%\end{itemize}


%\subsection*{\emph{Selected Proceedings}}
%\begin{itemize}

%\item [$bullet$] Author for the Collaboration, `` title ``, \emph{conference} (year).

%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``New Results in Rare Allowed Muon and Pion Decays``, \emph{9$^{th}$ International Workshop on e+ e- Collisions "From phi to psi 2013"} (2014).
%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``New Studies of Allowed Pion and Muon Decays``, \emph{11$^{th}$ Conference on the Intersections of Particle and Nuclear Physics } (2012).
%\item [$\bullet$] D. Kawall for the New Muon g-2 Collaboration, ``The New Muon g-2 Experiment at Fermilab'', \emph{11$^{th}$ Conference on the Intersections of Particle and Nuclear Physics (2012)}, \emph{AIP Conf.Proc. 1560 (2013) 106-108} (2013)
%\item [$\bullet$] S. Baessler for the Nab Collaboration, ``Neutron Beta Decay Studies with Nab``, \emph{11$^{th}$ Conference on the Intersections of Particle and Nuclear Physics } (2012).
%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``Rare Pion and Muon Decay Measurements: The PIBETA and PEN Experiments``, \emph{6$^{th}$ International Workshop on Chiral Dynamics} (2009).
%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``PEN Experiment: A Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Decay Branching Fraction``, \emph{10$^{th}$ Conference on the Intersections of Particle and Nuclear Physics conference} (2009).

%\item [$\bullet$] A. Palladino for the PEN Collaboration, ``Maximum Likelihood Analysis for the PEN Experiment'', \emph{April APS Meeting} (2010).

%\item [$\bullet$] A. Palladino for the PEN collaboration, ``The PEN Experiment at PSI: Testing Lepton Universality'', \emph{Seminar on Particle and Astrophysics, Universit\"at Z\"urich} (2010).

%\item [$\bullet$] L. Barron-Palos, et al., ``Measurement of parity-violating neutron capture gamma asymmetries at low-energies'' XXXII Symposium on Nuclear Physics, Revista Mexicana de Fisica Vol. 55, 2 (2009) 18-22.

%Barron-Palos L, Alarcon R, Alonzi LP, B.Lauss, et al. ``Measurement of parity-violating neutron capture gamma asymmetries at low-energies'' XXXII Symposium on Nuclear Physics, Hotel Hacienda, Morelos, Mexico, January 5-8,2009, Revista Mexicana De Fisica Vol. 55, 2 (2009) 18-22.


%\item [$\bullet$] E. Frle\v{z} for the PEN collaboration, ``Central Particle Tracking Detectors in the PEN Experiment'', \emph{Fall APS DNP Meeting} (2008).

%\item [$\bullet$] E. Frle\v{z} for the PEN collaboration, ``Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Branching Ratio'', \emph{New Trends in High Energy Physics, Yalta} (2008).

%\item [$\bullet$] S. Ritt for the PEN collaboration, ``Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Branching Ratio'', \emph{Swiss Institute for Particle Physics Annual Meeting (CHIPP)} (2008).

%\item [$\bullet$] D. Po\v{c}ani\'c for the Nab Collaboration,  ``Nab: Measurement Principles, Apparatus and Uncertainties'',  \emph{International Workshop for Particle Physics with Slow Neutrons} (2008).

%\item [$\bullet$] A. Palladino for the PEN collaboration, ``Waveform Analysis for a Precision Pion Decay Measurement'', \emph{Fall APS DNP Meeting} (2008).

%\item [$\bullet$] D. Po\v{c}ani\'c for the Nab Collaboration, ``The Nab Neutron Decay Correlation Experiment'', \emph{American Conference on Neutron Scattering} (2008).

%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``PEN: A Sensitive Search for Non-(V-A) Weak Process'', \emph{18$^{th}$ International Conference on Particles and Nuclei} (2008).

%\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``Rare Pion and Muon Decays: Summary of Results and Prospects'', \emph{Low Energy Precision Electroweak Physics in the LHC Era} (2008).


%\end{itemize}
