\documentclass{article}[10pt]
\usepackage{upgreek}
\usepackage{hyperref}
\usepackage{verbatim}


\begin{document}
\begin{center}
{\LARGE \textbf{Loreto Peter Alonzi III} }

\vspace{0.5cm}

\begin{tabular}{lclr}
\hline
\hline
\href{https://datascience.virginia.edu/}{School of Data Science}         & \qquad \qquad &  &         \\
\href{virginia.edu}{University of Virginia}        & \qquad \qquad &Phone: &   (434) 924-7835      \\
1919 Ivy Road, rm 344              & \qquad \qquad & Email: & alonzi@virginia.edu \\
Charlottesville, VA 22903& \qquad \qquad &  ORCID:      &    https://orcid.org/0000-0002-4525-3592                 \\
\hline
\hline
\end{tabular}
\end{center}


\section*{Professional Experience}
\begin{itemize}
\item [$\bullet$] Assistant Professor of Data Science, General Faculty, University of Virginia, 2022 August -present
\item [$\bullet$] Open Data Lab Project Manager and Data Scientist, School of Data Science, University of Virginia, 2018 October - 2022 August
\item [$\bullet$] Senior Research Data Scientist, Research Data Services, University Library, 2014 October - 2018 October
\end{itemize}


\section*{Education}
\begin{itemize}
\item [$\bullet$] Postdoctoral Research Associate, University of Washington, Department of Physics, Center for Experimental Nuclear Physics and Astrophysics, 2012 June - 2014 September
\item [$\bullet$] Ph.D. Physics, \href{http://www.phys.virginia.edu/}{\emph{University of Virginia}}, 2012.
\item [$\bullet$] M.A. Physics, \emph{University of Virginia}, 2007.
\item [$\bullet$] B.S. Physics with Honors et Magna cum Laude, \href{http://www.wm.edu/}{\emph{The College of William and Mary in Virginia}}, 2005.
\end{itemize}


\section*{Honors and Awards}
\begin{itemize}
\item [$\bullet$] SEDSI Best Paper in Innovation Track, The Future of Data Science Education, 2024
\item [$\bullet$] SEIDS Best Paper, 2024.
\item [$\bullet$] University of Virginia Society of Fellows, Junior Fellow, 2010.
\item [$\bullet$] Eagle Scout, BSA NEIC Troop 5, 1999.
\end{itemize}


\section*{Publications and Scholarly Work}
\subsection*{\emph{Archival Peer Reviewed Journal Articles}}
\begin{itemize}
\item [$\bullet$] M.A.McCulloch, {\bf L. P. Alonzi}, S. C. White, F. Haregu, and M. D. Porter. “Pediatric Donor Heart Acceptance Practices in the United States: What Is Really Being Considered?” Pediatric Transplantation 28, no. 1 (November 2023). https://doi.org/10.1111/petr.14649.
\item [$\bullet$] {\bf \LARGE Top Journal, 1,849 citations} -- B. Abi, et al. "Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm" (Muon $g-2$ Collaboration) Phys. Rev. Lett. 126, 141801 (2021)
\item [$\bullet$] J. Grigsby, et al. "Deep learning analysis of deeply virtual exclusive photoproduction" Phys. Rev. D 104, 016001 (2021)
\item [$\bullet$] {\bf \LARGE Top Journal} -- D. Blyth, et al. "First Observation of P-odd $\gamma$ Asymmetry in Polarized Neutron Capture on Hydrogen" (NPDGamma Collaboration) Phys. Rev. Lett. 121, 242002 (2018)
\item [$\bullet$] D. Po\v{c}ani\'c, et al. "PEN: a low energy test of lepton universality", \emph{PoS HQL} 2016 (2017) 042
\item [$\bullet$] {\bf L.P.Alonzi}, et al. "The calorimeter system of the new muon $g-2$ experiment at Fermilab", \emph{Nucl.Instrum.Meth. A} 824 (2016) 718-720
\item [$\bullet$] Muon $g-2$ collaboration, "The Measurement of the Anomalous Magnetic Moment of the Muon at Fermilab", \emph{J.Phys.Chem.Ref.Data} 44 (2015) no.3, 031211
\item [$\bullet$] A.T. Fienberg, et al. "Studies of an array of PbF2 Cherenkov crystals with large-area SiPM readout", \emph{Nucl.Instrum.Meth. A} 783 12-21 (2015)
\item [$\bullet$] D. Po\v{c}ani\'c, et al. ``Nab: Measurement Principles, Apparatus and Uncertainties'', \href{http://www.sciencedirect.com/science?_ob=ArticleURL&_udi=B6TJM-4WY6JS6-B&_user=709071&_coverDate=12/11/2009&_rdoc=1&_fmt=high&_orig=search&_origin=search&_sort=d&_docanchor=&view=c&_searchStrId=1563612201&_rerunOrigin=google&_acct=C000039638&_version=1&_urlVersion=0&_userid=709071&md5=602265f8ed1e05dbcd605115545a0871&searchtype=a}{\emph{Nucl.Instrum.Meth. A} 611, 211-215} (2009).

\item [$\bullet$] D. Počanić(Virginia U.), L.P. Alonzi(Virginia U.), V.A. Baranov(Dubna, JINR), W. Bertl(PSI, Villigen), Yu.M. Bystritsky(Dubna, JINR) et al. (PEN Collaboration), \href{https://inspirehep.net/literature/1705214}{Investigation of Rare Pion Decays with the PIBETA Spectrometer}, \emph{Phys.Part.Nucl.Lett. 15 6, 610-620} (2018).

\item [$\bullet$] {\bf \LARGE Top Journal} -- NPDGamma Collaboration, \href{https://inspirehep.net/literature/1683923}{First Observation of $P$-odd $\gamma$ Asymmetry in Polarized Neutron Capture on Hydrogen}, \emph{Phys.Rev.Lett 121 24 242002} (2018).

\item [$\bullet$] E. Frlez L.P. Alonzi for the PEN Collaboration, \href{https://inspirehep.net/literature/805323}{Precise Measurement of $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Branching Ratio}, \emph{New Trends in High-Energy Physics 2008, 97-106} (2008).


\end{itemize}

\section*{Archival peer reviewed conference proceedings, books, book chapters, and other categories}


\begin{itemize}

\item [$\bullet$] B. Wright, {\bf L. P. Alonzi}, A. Rivera. “The Future of Data Science Education” 53rd Annual Southeast Decision Science Institute (March 2024). Best paper in innovation track. https://arxiv.org/abs/2407.11824.

\item [$\bullet$] B. Wright, {\bf L. P. Alonzi}, A. Rivera. “What story can you tell from your cell phone apps?: A Data Science Lab Exercise” 53rd Annual Southeast Decision Science Institute (March 2024).


%\item [$\bullet$] "Introduction to R", DAACS Open Academy, Fall 2021
%\item [$\bullet$] "What Entropy and Impedance Mean in Data Science", Jefferson Lab AI Lunch Series, November 2020
\item [$\bullet$] "Machine Learning for global fitting of CFF from sparse data", Data Science Roadmap to compton form factors of quarks and gluons, Center for Nuclear Femtography, September 2020.
\item [$\bullet$] "Data Science and Femtography", CNF2019 Symposium, SURA Headquarters, August 2019.
%\item [$\bullet$] "Intro to Data Science", CSInstitute, July 2019.
\item [$\bullet$] ``The New Muon g-2 Experiment: E989 Status and Progress Update'', SESAPS 81st annual meeting, November 2014.
%\item [$\bullet$] ``Using the Library to Advance Scientific Data Practices'', University of Virginia, July 2014.
\item [$\bullet$] L.P. Alonzi for the PEN Collaboration, ``Precision Measurements of Rare Pion Decay Channels'', University of Washington, CENPA, March 2012.
%\item [$\bullet$] L.P. Alonzi for the Nab Collaboration, ``Precision Measurement of \emph{a} and \emph{b} in Neutron Beta Decay'', University of Virginia, January 2009.
\item [$\bullet$] L.P. Alonzi for the g-2 Collaboration, \href{http://pen.phys.virginia.edu/lpa2a-docs/2014-05-02-Alonzi-APSNWSection.pdf}{``The New Muon g-2 Experiment: E989 Status and Progress Update''}, \emph{APS NW Section Meeting} (2014).
\item [$\bullet$] L.P. Alonzi for the PEN Collaboration, \href{http://pen.phys.virginia.edu/talks/2010_April_APS_alonzi.pdf}{``A Mini Time Projection Chamber of the PEN Experiment''}, \emph{April APS Meeting} (2010).

\item [$\bullet$] C.J. Glaser for the PEN Collaboration, \href{https://inspirehep.net/literature/1706145}{`PEN experiment: a precise test of lepton universality''}, \emph{CIPANP} (2018).



\item [$\bullet$] L.P. Alonzi for the Nab Collaboration, \href{http://nab.phys.virginia.edu/slides/2009_April_APS_Alonzi.pdf}{``Precision Measurement of \emph{a} and \emph{b} in Neutron Beta Decay: The Nab/abBA Experimental Program''}, \emph{April APS Meeting} (2009).



\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, \href{https://inspirehep.net/literature/1287740}{``New Results in Rare Allowed Muon and Pion Decays``}, \emph{Int.J.Mod.Phys.Conf.Ser. 35 (2014) 1460437, 9$^{th}$ International Workshop on e+ e- Collisions "From phi to psi 2013"} (2014).





\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, \href{https://inspirehep.net/literature/1191427}{``New Results in Rare Allowed Muon and Pion Decays``}, \emph{AIP Conf.Proc. 1560 (2013) 1, 128-130 to CIPANP 2012} (2013).

\item [$\bullet$] S. Baessler for the NAB collaboration, \href{https://inspirehep.net/literature/1187655}{Neutron Beta Decay Studies with Nab}, \emph{AIP Conf.Proc. 1560 (2013) 1, 114-116 to CIPANP 2012} (2012).









\item [$\bullet$] D. Kawall for the New Muon g-2 Collaboration, ``The New Muon g-2 Experiment at Fermilab'', \emph{11$^{th}$ Conference on the Intersections of Particle and Nuclear Physics (2012)}, \emph{AIP Conf.Proc. 1560 (2013) 106-108} (2013)
\item [$\bullet$] S. Baessler for the Nab Collaboration, ``Neutron Beta Decay Studies with Nab``, \emph{11$^{th}$ Conference on the Intersections of Particle and Nuclear Physics } (2012).
\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``Rare Pion and Muon Decay Measurements: The PIBETA and PEN Experiments``, \emph{6$^{th}$ International Workshop on Chiral Dynamics} (2009).
\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``PEN Experiment: A Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Decay Branching Fraction``, \emph{10$^{th}$ Conference on the Intersections of Particle and Nuclear Physics conference} (2009).

\item [$\bullet$] A. Palladino for the PEN Collaboration, ``Maximum Likelihood Analysis for the PEN Experiment'', \emph{April APS Meeting} (2010).

\item [$\bullet$] A. Palladino for the PEN collaboration, ``The PEN Experiment at PSI: Testing Lepton Universality'', \emph{Seminar on Particle and Astrophysics, Universit\"at Z\"urich} (2010).

\item [$\bullet$] L. Barron-Palos, et al., ``Measurement of parity-violating neutron capture gamma asymmetries at low-energies'' XXXII Symposium on Nuclear Physics, Revista Mexicana de Fisica Vol. 55, 2 (2009) 18-22.

Barron-Palos L, Alarcon R, Alonzi LP, B.Lauss, et al. ``Measurement of parity-violating neutron capture gamma asymmetries at low-energies'' XXXII Symposium on Nuclear Physics, Hotel Hacienda, Morelos, Mexico, January 5-8,2009, Revista Mexicana De Fisica Vol. 55, 2 (2009) 18-22.


\item [$\bullet$] E. Frle\v{z} for the PEN collaboration, ``Central Particle Tracking Detectors in the PEN Experiment'', \emph{Fall APS DNP Meeting} (2008).

\item [$\bullet$] E. Frle\v{z} for the PEN collaboration, ``Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Branching Ratio'', \emph{New Trends in High Energy Physics, Yalta} (2008).

\item [$\bullet$] S. Ritt for the PEN collaboration, ``Precise Measurement of the $\uppi^{+}\rightarrow\mathrm{e}^{+}\nu$ Branching Ratio'', \emph{Swiss Institute for Particle Physics Annual Meeting (CHIPP)} (2008).

\item [$\bullet$] D. Po\v{c}ani\'c for the Nab Collaboration,  ``Nab: Measurement Principles, Apparatus and Uncertainties'',  \emph{International Workshop for Particle Physics with Slow Neutrons} (2008).

\item [$\bullet$] A. Palladino for the PEN collaboration, ``Waveform Analysis for a Precision Pion Decay Measurement'', \emph{Fall APS DNP Meeting} (2008).

\item [$\bullet$] D. Po\v{c}ani\'c for the Nab Collaboration, ``The Nab Neutron Decay Correlation Experiment'', \emph{American Conference on Neutron Scattering} (2008).

\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``PEN: A Sensitive Search for Non-(V-A) Weak Process'', \emph{18$^{th}$ International Conference on Particles and Nuclei} (2008).

\item [$\bullet$] D. Po\v{c}ani\'c for the PEN collaboration, ``Rare Pion and Muon Decays: Summary of Results and Prospects'', \emph{Low Energy Precision Electroweak Physics in the LHC Era} (2008).
\end{itemize}

\section*{h-index and citation count}
\begin{itemize}
\item [$\bullet$] h-index: 10 -- see \href{https://inspirehep.net/authors/1191633}{Profile on inSPIREHEP}
\item [$\bullet$] citation count: 2,548 -- see \href{https://inspirehep.net/authors/1191633}{Profile on inSPIREHEP}
\end{itemize}


\section*{Graduate Students} % name,status,recent milestone year, placement
\subsection*{Doctoral}
\begin{itemize}
\item [$\bullet$] Michael Murray, University of Washington, Graduated PhD 2017, Current: Lead Data Scientist at OneBridge Solutions
\item [$\bullet$] Matthias Smith, University of Washington, Graduated PhD 2017, Current: ML Scientist at Flexport 
\item [$\bullet$] Aaron Feinberg, University of Washington, Graduated PhD 2019, Current: Machine Learning Researcher at BlackBerry
\end{itemize}


\section*{Undergraduate Students} % name
\begin{itemize}
\item [$\bullet$] Kazimir Wall, University of Washington,  $g-2$
\item [$\bullet$] Aditi Jain, UVA,  $EBDM$
\item [$\bullet$] Amelia Norman, UVA. $EBDM$
\item [$\bullet$] Michela Nardi, UVA. $EBDM$
\item [$\bullet$] Carter Levinson, UVA. $EBDM$
\item [$\bullet$] Meredith Lawrence, UVA. $EBDM$
\item [$\bullet$] Audrey Kamauff, UVA. $EBDM$
\item [$\bullet$] James Wilby, UVA. $EBDM$
\item [$\bullet$] William Burge, UVA. $EBDM$
\item [$\bullet$] Paul Dalton, UVA. $EBDM$
\item [$\bullet$] Kathryn Murray, UVA. $EBDM$
\item [$\bullet$] Thomas Owen, UVA. $EBDM$
\item [$\bullet$] Charles Rowe, UVA. $EBDM$
\item [$\bullet$] Ashwin Sundaram, UVA. $EBDM$
\item [$\bullet$] Adam Will , UVA. $EBDM$
\item [$\bullet$] Emma Boland, UVA. $EBDM$
\item [$\bullet$] Caroline O’Brien, UVA. $EBDM$
\item [$\bullet$] John Henry Oliphant, UVA. $EBDM$
\item [$\bullet$] Josh Williams, UVA. $EBDM$
\item [$\bullet$] Henry Bramham, UVA. $EBDM$
\item [$\bullet$] Claire Deaver, UVA. $EBDM$
\item [$\bullet$] Sean Domnick, UVA. $EBDM$
\item [$\bullet$] Emma Hand, UVA. $EBDM$
\item [$\bullet$] Emily Ledwith, UVA. $EBDM$
\item [$\bullet$] Noah O’Neill, UVA. $EBDM$
\item [$\bullet$] Callie Weiler, UVA. $EBDM$
\item [$\bullet$] Bella Lu, UVA, $EBDM$, https://orcid.org/0009-0007-6152-072X
\item [$\bullet$] Grace Boland, UVA. $EBDM$
\item [$\bullet$] Colin Cool, UVA. $EBDM$
\item [$\bullet$] Nathaniel Donkoh-Moore, UVA. $EBDM$
\item [$\bullet$] Patrick Leonard, UVA. $EBDM$
\item [$\bullet$] Maddie McNult, UVA. $EBDM$
\item [$\bullet$] George Corbin, UVA. $EBDM$
\item [$\bullet$] Nora Dale, UVA. $EBDM$
\item [$\bullet$] Aatmika Deshpande, UVA. $EBDM$
\item [$\bullet$] Katherine Korngiebel, UVA. $EBDM$
\item [$\bullet$] Paige Krablin, UVA. $EBDM$
\item [$\bullet$] Emma Wilt, UVA. $EBDM$
\item [$\bullet$] Stella Banino, UVA. $EBDM$
\item [$\bullet$] Chris Craft, UVA. $EBDM$
\item [$\bullet$] Laura Phillips, UVA. $EBDM$
\item [$\bullet$] Sally Sydnor, UVA. $EBDM$
\item [$\bullet$] George Boulos, UVA. $EBDM$
\item [$\bullet$] Josh Dornfeld, UVA. $EBDM$
\item [$\bullet$] Imani Hankinson, UVA. $EBDM$
\item [$\bullet$] Livia Hughes, UVA. $EBDM$
\item [$\bullet$] Sarah Murphy, UVA. $EBDM$
\item [$\bullet$] Ronica Peraka, UVA. $EBDM$
\item [$\bullet$] McBride Rawson, UVA. $EBDM$
\end{itemize}

\section*{Funded and Under Review Grant Proposals as PI/Co-PI}
\begin{itemize}

\item[$\bullet$] Criminal Justice Data Training Center (2024) \$191,562 total and targeted
\begin{itemize}
\item[$\bullet$] (PI) {\bf L.P.Alonzi}
\item[$\bullet$] The Jefferson Trust, pending review Jan 2015- Dec 2017
\end{itemize}


\item[$\bullet$] Building Inclusive Student-Informed Courses (2023) \$9,600
\begin{itemize}
\item[$\bullet$] (PI) R. Schmidt; (Co-PI): {\bf L.P.Alonzi}
\item[$\bullet$] Inclusive Excellence award from UVA Division for Diversity, Equity, and Inclusion
\end{itemize}
\item[$\bullet$] Data Science Active Learning Lab (2022) \$150,000
\begin{itemize}
\item[$\bullet$] (PI) B.Wright; (Co-PI): {\bf L.P.Alonzi}
\item[$\bullet$] President and Provost’s Fund for Institutionally Related Research
\end{itemize}
\item[$\bullet$] Optimizing pediatric donor heart utilization using big data analytics (2022) \$133,078
\begin{itemize}
\item[$\bullet$] (PI) M.McCulloch; (Co-PI): {\bf L.P.Alonzi}, M. Porter
\item[$\bullet$] Jefferon Trust
\end{itemize}
\item[$\bullet$] SIWIF: Summer Institute on Wigner Imaging and Femtography (2019) \$50,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2020-FEMT-006-05 (continuation supplemental)
\end{itemize}
\item[$\bullet$] SIWIF: Summer Institute on Wigner Imaging and Femtography (2019) \$30,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2020-FEMT-006-05
\end{itemize}
\end{itemize}\begin{itemize}
\item[$\bullet$] Wigner Imaging (2018) \$50,000
\begin{itemize}
\item[$\bullet$] (PI) S.Liuti; (Co-PIs): {\bf L.P.Alonzi}, M.Burkhardt, D.Keller, O.Pfister
\item[$\bullet$] Southeastern Universities Research Association, Inc. Grant Agreement No. C2019-FEMT-002-04
\end{itemize}
\end{itemize}



%-----------------------------------------------------------------------------------------------------------------------
%-----------------------------------------------------------------------------------------------------------------------

\section*{Presentations, Invited}


\begin{itemize}
\item [$\bullet$] "Introduction to R", DAACS Open Academy, Fall 2021
\item [$\bullet$] "What Entropy and Impedance Mean in Data Science", Jefferson Lab AI Lunch Series, November 2020
\item [$\bullet$] "Machine Learning for global fitting of CFF from sparse data", Data Science Roadmap to compton form factors of quarks and gluons, Center for Nuclear Femtography, September 2020.
\item [$\bullet$] "Data Science and Femtography", CNF2019 Symposium, SURA Headquarters, August 2019.
\item [$\bullet$] "Intro to Data Science", CSInstitute, July 2019.
\item [$\bullet$] ``The New Muon g-2 Experiment: E989 Status and Progress Update'', SESAPS 81st annual meeting, November 2014.
\item [$\bullet$] ``Using the Library to Advance Scientific Data Practices'', University of Virginia, July 2014.
\item [$\bullet$] L.P. Alonzi for the PEN Collaboration, ``Precision Measurements of Rare Pion Decay Channels'', University of Washington, CENPA, March 2012.
\end{itemize}

\section*{Internal Service}

\begin{itemize}
\item [$\bullet$] Undergraduate Committee, 2020-present, (School)
\item [$\bullet$] Academic Committee, 2023-present, (School)
\item [$\bullet$] Deputy Director of Undergraduate Programs, 2024-present (School)
\item [$\bullet$] Darden Collaboratory Steering Committee, 2022-present (School)
\item [$\bullet$] ADSTP Hiring Committee, 2023, (School)
\end{itemize}


\section*{Professional Services}
\begin{itemize}
\item [$\bullet$] Academic Data Science Alliance, Annual Meeting 2024, Program Committee
\item [$\bullet$] Center for Teaching Excellence, 2023 Innovations in Pedagogy Summit, Program Committe
\end{itemize}


\section*{ORCID}
\href{https://orcid.org/0000-0002-4525-3592}{https://orcid.org/0000-0002-4525-3592}




\section*{Teaching Experience}

Full record see: \href{https://github.com/alonzi/cv/blob/master/teaching-record.md}{github.com/alonzi/cv}







\begin{center} Updated: \today \end{center}



\end{document}
